Network segregation, Social Isolation and Preference for Redistribution across societies

### 2023-09-27 paper.Rmd
cloud

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = TRUE,    # cache de los chunks,usar analisis pesados
                      out.width = '100%',
                      fig.pos= "H",     # posicion figuras H = HERE
                      fig.align = "center",
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''
```

```{r}
old<- ggplot2::theme_set(theme_minimal())
ggplot2::theme_set(old)
ggplot2::theme_update(text=element_text(size=9,  family="serif"))
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
```

@@

```{r mod-homclass,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)") 
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,class5,
                        homclass,
                        Q05pcm,
                        Q03pcm,
                        # isei08,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        labst,
                        labst1,
                        isolation,
                        MAINSTAT,
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
  na.omit()
# dim(dfreg)

@@

@@

```{r ineq-homo,fig.height=4,fig.width=7.5,fig.cap=c("Network Homogeneity and Income Inequality in the ISSP 2017"), out.width = '50%'}
sizetext <- 2.5
resits_count <- dfreg %>%
  group_by(country2,country) %>%
  summarise_at(c("redist","homclass", 
                 "gini_disp","gini_mkt"), mean, na.rm = TRUE) %>% 
  as.data.frame()
resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
p1 <- resits_count %>%  
ggplot(aes(y=homclass, x=gini_disp)) +
  geom_text(label=as.character(resits_count$country3),size=sizetext) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Gini (Disposable)")+
  ylab("Class homogeneity") +
  labs(
    # title = "Class homogeneity and Income Inequality (Disposable)",
       caption =paste("r=",round(cor(resits_count$homclass,
                                     resits_count$gini_disp),digits = 2),""))
# cor.test(resits_count$homclass,resits_count$gini_disp)
p2 <- resits_count %>%  
ggplot(aes(y=homclass, x=gini_mkt)) +
  geom_text(label=as.character(resits_count$country3),size=sizetext) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Gini (Market)")+
  ylab("Class homogeneity") +
  labs(
    # title = "Class homogeneity and Income Inequality (Market)",
       caption =paste("r=",round(cor(resits_count$homclass,
                                     resits_count$gini_mkt),digits = 2),""))

@@

giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
# anova(giniM_gdp,giniM_rs)
giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)

giniOT_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1|country2),data=dfreg)
giniOT_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1+homclass|country2),data=dfreg)
# anova(giniOT_gdp,giniOT_rs)
giniOT_int <- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ giniot + logrgdpna+ (1+homclass|country2),data=dfreg)

models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int )

@@

# Predicted values 
predval1 <- 
plot_predictions(giniD_int, condition = list("homclass",gini_disp="threenum"),gray = T) +
  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
       linetype='Gini (Disposable)') +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

# Predicted values 
predval2 <- 
plot_predictions(giniM_int, condition = list("homclass",gini_mkt="threenum"),gray = T)+
  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
       linetype='Gini (Market)') +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")
```

@@

@@

# Predicted values 
predval1 <- 
plot_predictions(giniD_int, condition = list("isolation",gini_disp="threenum"),gray = T) +
  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
       linetype='Gini (Disposable)') +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

# Predicted values 
predval2 <- 
plot_predictions(giniM_int, condition = list("isolation",gini_mkt="threenum"),gray = T)+
  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
       linetype='Gini (Market)') +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")
```

```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction forPerceived Isolation and Gini (Disposable)"),out.width='50%'}
grid.arrange(p1,predval1,nrow = 1  
             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"
             )
```

@@

* The **Palma ratio** is the share of all income received by the 10% people with highest disposable income divided by the share of all income received by the 40% people with the lowest disposable income.
* **90/10 ratio** = the ratio of Decile 10 income to Decile 1 income
<!-- * 90/50 ratio = the ratio of Decile 10 income to Decile 5 income (the median) -->
<!-- * 50/10 ratio = the ratio of Decile 5 income (the median) to Decile 1 income. -->

```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_gc,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        gv_spen=gv_spen,
                        pc10_2017,pc50_2017,
                        ratio10_50,
                        palmawd,
                        rgdpna,
                        individualism,
                        edyears,
                        female,
                        agenum,
                        country2,
                        union,
                        labst,
                        labst1,
                        isolation,
                        MAINSTAT) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2)
    # filter(!country2 %in% c("Turkey","Estonia")) %>%
  # filter(MAINSTAT %in% c(1,2)) 
  # filter(agenum %in% c(25:65))

int_palma <- lmer(redist~class3+ isolation+homclass*palmawd+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
int_pc10  <- lmer(redist~class3+ isolation+homclass*pc10_2017+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
int_pc50  <- lmer(redist~class3+ isolation+homclass*pc50_2017+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
int_r1090 <- lmer(redist~class3+ isolation+homclass*ratio10_50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
# int_giniot<- lmer(redist~class3+ homclass*giniot+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
int_indivi<- lmer(redist~class3+ isolation+homclass*individualism+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
int_govspe<- lmer(redist~class3+ isolation+homclass*gv_spen+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)

models_m <- list(int_palma,int_pc10,int_pc50,int_r1090,int_indivi,int_govspe)

cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
customcoef <- 
list(homclass = "Class-based network homogeneity",
  logrgdpna           = "log GDP",
  palmawd               = "Palma Ratio",
  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
  pc10_2017             = "Share National Income - top 10%",
  "homclass:pc10_2017"    = "Homogeneity x top 10",
  pc50_2017             = "Share National Income -  bottom 50%",
  "homclass:pc50_2017"    = "Homogeneity x bottom 50",
  ratio10_50            = "Ratio (90/50)",
  "homclass:ratio10_50"   = "Homogeneity x Ratio (90/50)",
  individualism         = "Individualism Index*",
  "homclass:individualism" = "Homogeneity x Individualism",
  gv_spen               = "Gov. Spending (% GDP)*",
  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
)
texreg::knitreg(models_m,custom.coef.map = customcoef,caption.above = T,caption = cap1)
```

```{r,fig.height=4,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
# p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmawd") +
#   xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0) +
#     labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))

p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="pc10_2017") +
  xlab("Share National Income -  top 10%") + geom_point()+ geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(int_pc10),", Countries=",lme4::ngrps(int_pc10)))

p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="pc50_2017") +
  xlab("Share National Income - bottom 50%") + geom_point()+ geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))

p6<- interplot::interplot(m = int_r1090,var1 = "homclass",var2="ratio10_50") +
  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)+
  labs(caption = paste0("N=",nobs(int_r1090),", Countries=",lme4::ngrps(int_r1090)))  
grid.arrange(p4,p5,p6,nrow = 1)  
```

```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='70%'}
# p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
#   xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
#   labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))

@@

predval8 <- 
plot_predictions(int_indivi, condition = list("homclass",individualism="threenum"),gray = T) +
  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
       linetype='Individualism') +
  xlab("Class-based homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

@@

predval9 <- 
plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = T) +
  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
       linetype='Gov.Spend') +
  xlab("Class-based homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

@@

<!-- # (APPENDIX) Appendix {-}  -->

>>>>

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = F,    # cache de los chunks,usar analisis pesados
                      out.width = '100%',
                      fig.pos= "H",     # posicion figuras H = HERE
                      fig.align = "center",
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''
```

```{r}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(theme_minimal())
ggplot2::theme_update(text=element_text(size=10,  family="serif"))  
```

@@

```{r mod-homclass,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class3res <- relevel(df1$class3res,ref =  "Intermediate class (III+IV)") 
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,class5,
                        homclass,
                        Q05pcm,
                        Q03pcm,
                        # isei08,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        giniindex,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        labst,
                        labst1,
                        isolation,
                        MAINSTAT,
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("CHN")) %>%
  # filter(!country2 %in% c("TWN")) %>%
  # filter(!country2 %in% c("ZAF")) %>%
  # filter(!country2 %in% c("FIN")) %>%
  # filter(!country2 %in% c("USA")) %>%
  # filter(!country2 %in% c("GBR")) %>%
  # filter(!country2 %in% c("ISL")) %>%
  # filter(!country2 %in% c("TUR","EST")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
  na.omit()
# dim(dfreg)

@@

```{r leverage1, eval=FALSE, include=FALSE}
pacman::p_load(influence.ME,lattice)
# dfbetas-----------------------------------------------------------------------
influence <- influence(rob3, "country2")
dfbetas(influence,parameters=c(1,4)) 
n_groups <- lme4::ngrps(rob3)

influence_est=as.data.frame(dfbetas(influence))
influence_est %>%  filter(homclass > 2/sqrt(n_groups))

plot(influence, which="dfbetas", 
     parameters=c(1,4),
     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))

# cook-distance-----------------------------------------------------------------
# cooks.distance(rob3, sort = TRUE)
plot(influence, which="cook",
     cutoff=4/n_groups, sort=TRUE,
     xlab="Cooks Distance",
     ylab="Country")

sigtest1<- sigtest(influence, test=-1.96)
sigtest1$homclass
```

@@

```{r ineq-homo,fig.height=4,fig.width=7.5,fig.cap=c("Network Homogeneity and Income Inequality in the ISSP 2017"), out.width = '50%'}
sizetext <- 2.5
resits_count <- dfreg %>%
  group_by(country2,country) %>%
  summarise_at(c("redist","homclass", 
                 "gini_disp","gini_mkt","giniindex"), mean, na.rm = TRUE) %>% 
  as.data.frame()
resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")
p1 <- resits_count %>%  
ggplot(aes(y=homclass, x=gini_disp)) +
  geom_text(label=as.character(resits_count$country3),size=sizetext) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Gini (Disposable)")+
  ylab("Class homogeneity") +
  labs(
    # title = "Class homogeneity and Income Inequality (Disposable)",
       caption =paste("r=",round(cor(resits_count$homclass,
                                     resits_count$gini_disp),digits = 2),""))
# cor.test(resits_count$homclass,resits_count$gini_disp)
p2 <- resits_count %>%  
ggplot(aes(y=homclass, x=gini_mkt)) +
  geom_text(label=as.character(resits_count$country3),size=sizetext) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Gini (Market)")+
  ylab("Class homogeneity") +
  labs(
    # title = "Class homogeneity and Income Inequality (Market)",
       caption =paste("r=",round(cor(resits_count$homclass,
                                     resits_count$gini_mkt),digits = 2),""))

@@

giniM_gdp<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
giniM_rs<- lmer(redist~class3+ homclass+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
# anova(giniM_gdp,giniM_rs)
giniM_int <- lmer(redist~class3+ homclass*gini_mkt+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+homclass|country2),data=dfreg)
# anova(giniOT_gdp,giniOT_rs)

@@

# Predicted values 
predval1 <- 
plot_predictions(giniD_int, condition = list("homclass",gini_disp=range),gray = F) +
  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
       colour='Gini (Disposable)',fill='Gini (Disposable)') +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

# Predicted values 
predval2 <- 
plot_predictions(giniM_int, condition = list("homclass",gini_mkt=range),gray = F)+
  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
       colour='Gini (Disposable)',fill='Gini (Disposable)') +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")
```

@@

```{r leverage2, eval=FALSE, include=FALSE}
pacman::p_load(influence.ME,lattice)
# dfbetas-----------------------------------------------------------------------
influence <- influence(rob3, "country2")
dfbetas(influence,parameters=c(1,4)) 
n_groups <- lme4::ngrps(rob3)

influence_est=as.data.frame(dfbetas(influence))
influence_est %>%  filter(homclass > 2/sqrt(n_groups))

plot(influence, which="dfbetas", 
     parameters=c("isolation"),
     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))

# cook-distance-----------------------------------------------------------------
# cooks.distance(rob3, sort = TRUE)
plot(influence, which="cook",
     cutoff=4/n_groups, sort=TRUE,
     xlab="Cooks Distance",
     ylab="Country")

sigtest1<- sigtest(influence, test=-1.96)
sigtest1$homclass
```

@@

# Predicted values 
predval1 <- 
plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
       linetype='Gini (Disposable)') +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

# Predicted values 
predval2 <- 
plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
       linetype='Gini (Market)') +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")
```

```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='50%'}
grid.arrange(p1,predval1,nrow = 1    
             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
             )
```

@@

* The **Palma ratio** is the share of all income received by the 10% people with highest disposable income divided by the share of all income received by the 40% people with the lowest disposable income.
<!-- * **90/10 ratio** = the ratio of Decile 10 income to Decile 1 income -->
<!-- * 90/50 ratio = the ratio of Decile 10 income to Decile 5 income (the median) -->
<!-- * 50/10 ratio = the ratio of Decile 5 income (the median) to Decile 1 income. -->

```{r mod-other-macro,fig.height=3,fig.width=6,out.width='70%',results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_gc,
                        # homclass=homclass_res,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        giniindex,ttheilge1,
                        gv_spen=gv_spen,
                        top10,
                        middle50,
                        palmaratio,
                        rgdpna,
                        individualism,
                        edyears,
                        female,
                        agenum,
                        country2,
                        union,
                        labst,
                        labst1,
                        isolation,
                        MAINSTAT) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
    # filter(!country2 %in% c("Turkey","Estonia")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>%
   na.omit()

int_palma <- lmer(redist~class3+ isolation+homclass*palmaratio+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
int_pc10  <- lmer(redist~class3+ isolation+homclass*top10+edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
int_pc50  <- lmer(redist~class3+ isolation+homclass*middle50+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
int_gini_wiid  <- lmer(redist~class3+ isolation+homclass*giniindex+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
int_theil  <- lmer(redist~class3+ isolation+homclass*ttheilge1+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna +(1+homclass|country2),data=dfreg)
int_indivi<- lmer(redist~class3+ isolation+homclass*individualism+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
int_govspe<- lmer(redist~class3+ isolation+homclass*gv_spen+ edyears+ Q03pcm+ labst1+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)

models_m <- list(int_palma,int_pc10,int_pc50,int_indivi,int_govspe
                 # int_gini_wiid,int_theil
                 )

cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
customcoef <- 
list(homclass = "Class-based network homogeneity",
  logrgdpna           = "log GDP",
  palmaratio               = "Palma Ratio",
  "homclass:palmawd"      = "Homogeneity x Palma Ratio",
  top10             = "Share National Income - top 10%",
  "homclass:top10"    = "Homogeneity x top 10",
  middle50             = "Share National Income -  bottom 50%",
  "homclass:middle50"    = "Homogeneity x bottom 50",
  individualism         = "Individualism Index*",
  "homclass:individualism" = "Homogeneity x Individualism",
  gv_spen               = "Gov. Spending (% GDP)*",
  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
)
texreg::knitreg(models_m,
                custom.coef.map = customcoef,
                caption.above = T,caption = cap1)
```

```{r,fig.height=4,fig.width=12,fig.cap=c("Cross-level interaction for Network homogeneity and Economic Inequality"),out.width='100%',results='asis'}
p3<- interplot::interplot(m = int_palma,var1 = "homclass",var2="palmaratio") +
  xlab("Palma ratio (top 10%/ bottom 40%)") + geom_point()+ geom_hline(yintercept = 0) +
    labs(caption = paste0("N=",nobs(int_palma),", Countries=",lme4::ngrps(int_palma)))

# plot_predictions(int_palma, condition = list("homclass",palmaratio=range),gray = F) +
#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
#        linetype='Palma Ratio') +
#   xlab("Class-based homogeneity")+
#   ylab("Redistributive preferences") +
#   theme(legend.position = "right")

p4<- interplot::interplot(m = int_pc10,var1 = "homclass",var2="top10") +
  xlab("Share National Income -  top 10%") + geom_point()+ geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(int_pc10),", Countries=",lme4::ngrps(int_pc10)))

# plot_predictions(int_pc10, condition = list("homclass",top10=range),gray = F) +
#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
#        linetype='Palma Ratio') +
#   xlab("Class-based homogeneity")+
#   ylab("Redistributive preferences") +
#   theme(legend.position = "right")
p5<- interplot::interplot(m = int_pc50,var1 = "homclass",var2="middle50") +
  xlab("Share National Income - middle 50%") + geom_point()+ geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(int_pc50),", Countries=",lme4::ngrps(int_pc50)))

# plot_predictions(int_pc50, condition = list("homclass",middle50=range),gray = F) +
#   labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
#        linetype='Palma Ratio') +
#   xlab("Class-based homogeneity")+
#   ylab("Redistributive preferences") +
#   theme(legend.position = "right")

# interplot::interplot(m = int_gini_wiid,var1 = "homclass",var2="giniindex") +
#   xlab("Gini (WIID)") + geom_point()+ geom_hline(yintercept = 0) +
#     labs(caption = paste0("N=",nobs(int_gini_wiid),", Countries=",lme4::ngrps(int_gini_wiid)))

# interplot::interplot(m = int_theil,var1 = "homclass",var2="ttheilge1") +
#   xlab("Theil Index") + geom_point()+ geom_hline(yintercept = 0) +
#     labs(caption = paste0("N=",nobs(int_theil),", Countries=",lme4::ngrps(int_theil)))

# p6<- interplot::interplot(m = int_r1090,var1 = "homclass",var2="ratio10_50") +
#   xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)+
#   labs(caption = paste0("N=",nobs(int_r1090),", Countries=",lme4::ngrps(int_r1090)))  
grid.arrange(p3,p4,p5,nrow = 1) 
```

```{r , fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='70%',}
# p7<- interplot::interplot(m = int_giniot,var1 = "homclass",var2="giniot") +
#   xlab("Gini Market*") + geom_point()+ geom_hline(yintercept = 0)+
#   labs(caption = paste0("N=",nobs(int_giniot),", Countries=",lme4::ngrps(int_giniot)))

@@

predval8 <- 
plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
       linetype='Individualism') +
  xlab("Class-based homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

@@

predval9 <- 
plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
       linetype='Gov.Spend') +
  xlab("Class-based homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

@@
